The evolution of gene expression in the term placenta of viviparous mammals

### 2015-12-15 manuscript/manuscript.Rnw
clean up text in gene tables

<<top.genes.function,echo=FALSE,results="hide">>=
top.genes.table <- function(species.name,n=50) {
    temp <- 
        combined.fpkm[species==species.name &
                           !(!is.na(human_name) & 
                                 human_name %in% housekeeping.genes.superset[,gene_short_name]) &
                               !grepl("((RNA\\d|MT)-|^RP[SL]\\d+$)",human_name) &
                                   !grepl("(^[Mm][Tt]-|^R[pP][lsLS]\\d+[abcdABCD]?[l]?(?:-.+)?$|rRNA$)",gene_short_name)
                      ][order(-mean_fpkm)][,list(name_or_id,
                                                 human_name,mean_fpkm)]
    ## remove any genes which have a null name_or_id; they are probably from unassembled contigs
    temp <- temp[!(is.na(name_or_id)|name_or_id==""),]
    temp <- temp[!duplicated(name_or_id)][1:n]
    setkey(temp,"human_name")
    temp <- 
        hugo.nomenclature[temp][order(-mean_fpkm),
                                list(name_or_id,`Approved Symbol`,`Approved Name`,mean_fpkm)]
    temp[!is.na(`Approved Name`),
         `Approved Name`:=paste0("\\href{http://www.ensembl.org/Homo_sapiens/Gene/Summary?g=",`Approved Symbol`,"}{",xtable.sanitize.text(`Approved Name`),"}")]
    temp[!is.na(`Approved Symbol`),
         `Approved Symbol`:=paste0("\\href{http://www.ensembl.org/Homo_sapiens/Gene/Summary?g=",`Approved Symbol`,"}{",xtable.sanitize.text(`Approved Symbol`),"}")]
    setnames(temp,c("Gene symbol","Human Symbol","Human Name","FPKM"))
    if (species.name=="homo sapiens") {
        temp <- temp[,-2,with=FALSE]
    }
    return(temp)
}
genes.table.sanitize <- function(str){
    return(str)
}
xtable.sanitize.text <- function(str){
    result <- str
    result <- gsub("\\\\", "SANITIZE.BACKSLASH", result)
    result <- gsub("$", "\\$", result, fixed = TRUE)
    result <- gsub(">", "$>$", result, fixed = TRUE)
    result <- gsub("<", "$<$", result, fixed = TRUE)
    result <- gsub("|", "$|$", result, fixed = TRUE)
    result <- gsub("{", "\\{", result, fixed = TRUE)
    result <- gsub("}", "\\}", result, fixed = TRUE)
    result <- gsub("%", "\\%", result, fixed = TRUE)
    result <- gsub("&", "\\&", result, fixed = TRUE)
    result <- gsub("_", "\\_", result, fixed = TRUE)
    result <- gsub("#", "\\#", result, fixed = TRUE)
    result <- gsub("^", "\\verb|^|", result, fixed = TRUE)
    result <- gsub("~", "\\~{}", result, fixed = TRUE)
    result <- gsub("SANITIZE.BACKSLASH", "$\\backslash$",
                   result, fixed = TRUE)
    return(result)
}
gene.expression <- function(species.name,gene,complete=FALSE) {
    fpkm <- combined.fpkm[species==species.name &
                              gene_short_name==gene,
                          mean_fpkm]

>>>>

<<top.genes.function,echo=FALSE,results="hide">>=
top.genes.table <- function(species.name,n=50) {
    temp <- 
        combined.fpkm[species==species.name &
                           !(!is.na(human_name) & 
                                 human_name %in% housekeeping.genes.superset[,gene_short_name]) &
                               !grepl("((RNA\\d|MT)-|^RP[SL]\\d+$)",human_name) &
                                   !grepl("(^[Mm][Tt]-|^R[pP][lsLS]\\d+[abcdABCD]?[l]?(?:-.+)?$|rRNA$)",gene_short_name)
                      ][order(-mean_fpkm)][,list(name_or_id,
                                                 human_name,mean_fpkm)]
    ## remove any genes which have a null name_or_id; they are probably from unassembled contigs
    temp <- temp[!(is.na(name_or_id)|name_or_id==""),]
    temp <- temp[!duplicated(name_or_id)][1:n]
    setkey(temp,"human_name")
    temp <- 
        hugo.nomenclature[temp][order(-mean_fpkm),
                                list(name_or_id,`Approved Symbol`,`Approved Name`,mean_fpkm)]
    temp[!is.na(`Approved Name`),
         `Approved Name`:=paste0("\\href{http://www.ensembl.org/Homo_sapiens/Gene/Summary?g=",`Approved Symbol`,"}{",xtable.sanitize.text(`Approved Name`),"}")]
    temp[!is.na(`Approved Symbol`),
         `Approved Symbol`:=paste0("\\href{http://www.ensembl.org/Homo_sapiens/Gene/Summary?g=",`Approved Symbol`,"}{",xtable.sanitize.text(`Approved Symbol`),"}")]
    if (species.name=="homo sapiens") {
        temp[,name_or_id:=paste0("\\href{http://www.ensembl.org/Homo_sapiens/Gene/Summary?g=",name_or_id,"}{",xtable.sanitize.text(name_or_id),"}")]
    } else {
        temp[,name_or_id:=xtable.sanitize.text(name_or_id)]
    }
    setnames(temp,c("Gene symbol","Human Symbol","Human Name","FPKM"))
    if (species.name=="homo sapiens") {
        temp <- temp[,-2,with=FALSE]
    }
    return(temp)
}
genes.table.sanitize <- function(str){
    return(str)
}
xtable.sanitize.text <- function(str){
    result <- str
    result <- gsub("\\\\", "SANITIZE.BACKSLASH", result)
    result <- gsub("$", "\\$", result, fixed = TRUE)
    result <- gsub(">", "$>$", result, fixed = TRUE)
    result <- gsub("<", "$<$", result, fixed = TRUE)
    result <- gsub("|", "$|$", result, fixed = TRUE)
    result <- gsub("{", "\\{", result, fixed = TRUE)
    result <- gsub("}", "\\}", result, fixed = TRUE)
    result <- gsub("%", "\\%", result, fixed = TRUE)
    result <- gsub("&", "\\&", result, fixed = TRUE)
    result <- gsub("_", "\\_", result, fixed = TRUE)
    result <- gsub("#", "\\#", result, fixed = TRUE)
    result <- gsub("^", "\\verb|^|", result, fixed = TRUE)
    result <- gsub("~", "\\~{}", result, fixed = TRUE)
    result <- gsub("SANITIZE.BACKSLASH", "$\\backslash$",
                   result, fixed = TRUE)
    return(result)
}
gene.expression <- function(species.name,gene,complete=FALSE) {
    fpkm <- combined.fpkm[species==species.name &
                              gene_short_name==gene,
                          mean_fpkm]
